%% start of file `template.tex'.
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%% Copyright 2010-2011 Mark Liu (markwayneliu@gmail.com).
%% Copyright 2015 Joseph Daigle (joseph.daigle@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,letterpaper,sans]{moderncv}

\usepackage{verbatim}

% moderncv themes
\moderncvstyle{classic}
\moderncvcolor{blue}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.81]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths


% personal data
\firstname{Joseph}
\familyname{Daigle}
\email{joseph.daigle@gmail.com}
\phone{+1~(678)~296~6166}
\extrainfo{%
  \homepagesymbol\url{stackoverflow.com/users/507/joseph-daigle} \\
  \homepagesymbol\url{github.com/jdaigle}
}

% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Technical Experience}
\subsection{Extremely Proficient With}
\cvline{languages}{C\#, XML/XLST, T-SQL, JavaScript, HTML, CSS, Java}
\cvline{technologies}{GIT, Subversion, ASP.NET, Windows Server, IIS, MS SQL Server, JQuery, NHibernate, NServiceBus, Active Directory, Exchange Server, HAProxy, JIRA, TeamCity}
\subsection{Have Experience With}
\cvline{languages}{VB.NET, C, C++, PHP, Ruby, Smalltalk, Scheme, Python, Perl, F\#}
\cvline{technologies}{PostgreSQL, Redis, OSX, Linux/CentOS, Apache, Tomcat, Mercurial, TFS, ESRI, Lucene, Solr, ElasticSearch, Cassandra, RavenDB, AngularJS, Azure, AWS}

\section{Experience}
\cventry{2013--Present}{Software Architect / Director of Development}{Clearwave Corporation}{Atlanta, GA}{}{
\url{http://www.clearwaveinc.com/}\newline{}\newline{}
Promoted to a position to manage the entire software development team and software development life-cycle. Responsibilities include hiring new developers, mentoring both junior and senior developers, managing the backlog of product requirements and feature requests, managing the release schedule, leading code reviews and sprint planning meetings, and maintaining architectural consistency across all products and applications. Day-to-day activities require keeping developers productive by reducing the overhead of meetings and disruptions, as well as continuing to work side-by-side with developers to guide development of new features. Additionally tasked to work with technology partners to integrate their technology into Clearwave's, or vice versa.\newline{}\newline{}
\textbf{Achievements:}
\begin{itemize}
\item Introduced guidelines for client implementations team to build requirements and specifications for back-end integrations, such as HL7 and VPN connections.
\item Implemented a QA workflow that includes automated unit tests and full integration tests as well as manual acceptance and regression testing.
\item In charge of researching and building requirements for the servers and network equipment as part of a major data center upgrade. Tasked to execute the final migration of applications, databases, and network connections between data centers.
\item Architected a new application database schema, and designed and developed the data migration process. The goal of this project is to align the data model with business needs in terms of performance, scalability, and auditing.
\item Worked to normalize internal API design and data access patterns. Achieved a simpler back-end architecture that enables developers to implement new features faster and with fewer bugs.
\item Instrumented application level performance metrics to measure response times and to correlate with CPU and database query times. This lead to significant performance and scalability improvements in slow and high volume application operations.
\item Lead a team to design and build a new Provider Portal user interface targeting modern web browsers using a variety of modern web application techniques (e.g. HTML5, CSS, modern JavaScript, etc.)
\end{itemize}
}
\cvitem{}{}

\cventry{2009--2013}{Senior Software Engineer}{Clearwave Corporation}{Atlanta, GA}{}{
{\url{http://www.clearwaveinc.com/}}\newline{}\newline{}
Software development engineer working on patient registration solutions for healthcare providers. Primarily web applications hosted from a "cloud" data center. Back end solutions include EDI transactions for health insurance eligibility verification, payment processor integration, and bidirectional HL7 integrations for patient registration data flow to and from customer practice management systems.\newline{}\newline{}
\textbf{Achievements:}
\begin{itemize}
\item Introduced "agile" methodologies and TDD practices.
\item Worked on a team to design and implement a new HTML powered kiosk application to replace the aging Flash powered application. Server side frameworks and utilities include ASP.NET MVC and NHibernate. Client side scripting was handled through JQuery and various plug-ins.
\item Designed a custom "Kiosk Browser" using WinForms and an embedded IE Web Control that is installed on deployed kiosks and is used to interact with the kiosk web application.
\item Implemented kiosk hardware integrations including magnetic stripe readers (MSR) for payment and a camera for scanning driver's licenses and medical insurance cards.
\item Implemented a software solution to automatically scan and read information from driver's licenses and medical insurance cards through optical character recognition (OCR).
\item Redesigned Provider Portal application to use modern development strategies including ASP.NET MVC and client side scripting libraries such as JQuery.
\item Design and implemented a new EDI engine to integrate with healthcare insurance companies for electronic eligibility verification. The system is designed around NServiceBus utilizing a publish/subscribe architecture to scale to tens of thousands of transactions per day.
\end{itemize}
}
\cvitem{}{}

\cventry{2008--2009}{Software Engineer}{GeoFields, Inc.}{Atlanta, GA}{}{
{\url{http://www.geofields.com/}}\newline{}\newline{}
Enterprise software engineer for the industry leader in transmission pipeline data management software and services. Worked in multiple small teams that delivered a comprehensive enterprise software solution. Responsibilities included all aspects of the software process from design through development, quality assurance and release. Primarily utilized .NET, C\#, ASP.NET, ESRI ArcObjects, ESIR ArcDesktop, MS SQL Server, Oracle, and LLBLGen Pro.\newline{}\newline{}
\textbf{Achievements:}
\begin{itemize}
\item Lead developer on the DataFrame Data Maintenance (DFDM) product. The product is built as an extension to ESRI’s ArcMap application to maintain linearly-referenced transmission pipeline data in a customized geodatabase. The software consists of a .NET WinForms front end, written in C\#, with a shared back end library encapsulating the data access layer and domain object layer. Additionally, intense ArcObjects programming and business logic design was involved to build the user interface and interact with the data model. This product was demoed at the 2008 GeoFields User Conference.
\item Developer on the Facility Explorer (FE) product. An ASP.NET web application which utilizes ESRI mapping technology to dynamically display transmission pipeline assets, as well as a reporting tool. It relies heavily on custom JavaScript libraries to enable rich user interaction with the map. Also participated in support of a legacy classic ASP version of the software.
\item Lead the design and development of a large enterprise foundation code base to be reused by several other software applications. Much of the work included building a dynamic data access layer and business logic layer. Several newer .NET technologies were utilized including WCF and LINQ.
\end{itemize}
}
\cvitem{}{}

\cventry{2005-2007}{IT Analyst / IT Support Specialist}{Southern Regional Education Board}{Atlanta, GA}{}{
{\url{http://www.sreb.org/}}\newline{}\newline{}
Worked during alternating semesters via Georgia Tech's Cooperative Education Program. As an IT support specialist, supported 150 users and workstations. Additionally designed and implemented ASP.NET web applications for internal and external client projects.\newline{}\newline{}
\textbf{Achievements:}
\begin{itemize}
\item Designed and developed an internal content management system for the web and desktops based on Microsoft SharePoint. This utilized several custom ASP.NET web parts as well as integration with Active Directory for authentication and authorization. An ASP.NET web application was built to enable external user registration within an isolated Active Directory application domain, and email support.
\item Worked on several projects to create classic ASP and ASP.NET web surveys answered by thousands of students and educators across the country. A custom framework was designed to facilitate the implementation and deployment of these surveys for various teams within the organization.
\item Refined a Windows desktop imaging and deployment system to use a central imaging server and PXE booting.
\item Built a 1TB storage cluster with fail-over and data replication using DFS and DFSR to host and share thousands of internal documents and publications across the organization.
\end{itemize}
}
\cvitem{}{}

\cventry{2004}{Systems Support Specialist / IT Intern}{Porex Corporation}{Atlanta, GA}{}{
{\url{http://www.porex.com/}}\newline{}\newline{}
Responsibilities include supporting over 250 users and client workstations across work 3 work sites and systems administration of several Active Directory and Exchange servers.\newline{}\newline{}
\textbf{Achievements:}
\begin{itemize}
\item Designed and implemented a large scale user desktop imaging/deployment system utilizing Windows deployment technologies including sysprep and 3rd part tools such as Symantec Ghost.
\item Developer for a Java network monitoring system. Utilized several open source products including OpenNMS and other assets management tools, customized for the environment and monitoring requirements.
\end{itemize}
}
\cvitem{}{}

\section{Education}
\cventry{2003--2007}{BS, Computer Science}{Georgia Institute of Technology}{Atlanta, GA}{}{}
\cvitem{}{Specialized in Networks, Communication, and Systems.}

\end{document}
